Constant Error Rate Computational Fuzzy Extractors

### 2014-01-10 constantRate/ConstCompFuzzExt.tex
Revised intro

\title{Constant Error Rate Computational Fuzzy Extractors}
\author{Some people}
\begin{document}
\maketitle

%\begin{abstract} 
%We make computational fuzzy extractors better.
%\end{abstract}

\section{Introduction}\label{sec:introduction}
Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} derive stable keys from noisy data.  They are composed of two algorithms: \gen takes a source value $w_0$, and produces a key $r$ and a public value $p$, and \rep which takes a nearby value $w_1$ and $p$ producing the original key $r$.  Intuitively, they are two functions: information reconciliation~(to provide the same value with \emph{noisy} readings) and key derivation or privacy amplification~(to transform an entropic source into a uniform key).  Traditionally, these two functions were performed by two separate primitives: a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} and a randomness extractor~\cite{nisan1993randomness}.

For a fixed length key, there are two main parameters: the desired error tolerance and the required entropy of the source.  In the information-theoretic setting these two parameter are at odds.  Any increase error-tolerance requires a similar increase to the entropy of the source.  However, this does not need to be the case in the computational setting.  The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The only difference between a computational fuzzy extractor and a fuzzy extractor is the key is pseudorandom instead of statistically random. }  With computational security, an error tolerance \emph{larger} than the starting entropy may be possible.  We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance.\footnote{Security is impossible if all points of the source distribution are close together.  In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within any error-tolerance region.   This is both a necessary and sufficient condition for security in the interactive setting using two-party computation.}

Our construction is based on obfuscation.  While black-box obfuscation of polynomial time functions is known to be impossible~\cite{barak2001possibility}, we use the obfuscation of point functions.  This class is known to be achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and generically from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.

\textbf{Overview of Construction:}  Consider a source $w = w_1,..., w_\ell$ that is split into blocks.  We would like to construct tolerate Hamming errors for individual blocks.  The main idea is for each block, $i$: either the $w_i$ is obfuscated or a random point $r_i$ is obfuscated~(this idea is similar to the construction of digital lockers from point obfuscation).  Then with a close value $w'$ the recovery value knows where random values were obfuscated and where $w_i$ was obfuscated.  To tolerate errors, the choice of obfuscating $w_i$ or a random point is made using bits of an error correcting code.

\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a strictly stronger object than a computational fuzzy extractor).  Unfortunately, this is not the case.  Since each block is individual obfuscated, equality of individual blocks is learned~(for sources where not all blocks have high entropy).  This precludes virtual black-box~(VBB) security where no partial information about the input may be learned.  Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} constructed noisy point obfuscation when the source entropy is significantly higher than the error-tolerance.  Constructing VBB obfuscation for sources where the error tolerance is smaller than the starting entropy is an important open question.

\textbf{Our Results:} Specifically this paper presents the following:
\begin{itemize}
\item The first computational fuzzy extractor that supports a constant fraction of errors.
\item The first fuzzy extractor where the number of errors corrected is larger than the entropy of the starting distribution.
\end{itemize}
\bnote{More details here}

\bnote{Provide an outline of the rest of the paper}

\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $\mathcal{Z}$, we denote by $X_{1,..., k} = X_1||...|| X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.  For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.  For the Hamming metric, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).

@@

\subsection{Randomness Extractors and Computational Fuzzy Extractors}
\label{sec:fuzzy extractors}

Here we present relevant extractor definitions.  We start with the standard notion of an average-case extractor. An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

We focus on computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.  Definitions for information-theoretic fuzzy extractors and secure sketches can be found in the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.  The definition of computational fuzzy extractors allows for a small probability of error, as described in~\cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

%\begin{definition}
%\label{def:fuzzy extractor}
%An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties: 
%\begin{enumerate}
%\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
%\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
%\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
%\end{enumerate}
%A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
%\end{definition}
%
%Secure sketches are the main technical tool in the construction of fuzzy extractors.  Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
%\begin{definition}
%\label{def:secure sketch}
%An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
%\begin{enumerate}
%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
%\end{definition}
%

We now present the definition of a computational fuzzy extractor~(from~\cite{fuller2013computational}):

@@

\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\kappa$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.  
Note that in the above definition of fuzzy extractors, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
For notational convenience, we the definition of computational fuzzy extractors specifies a general class of sources for which the fuzzy extractor is designed to work, rather than the class of sources that consists of all sources of a given min-entropy $m$~(of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).

>>>>

\title{Constant Error Tolerance Computational Fuzzy Extractors\thanks{The work of B. Fuller is sponsored by Assistant Secretary of Defense for Research \& Engineering under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}}
\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin}

\begin{document}
\maketitle

\begin{abstract} 
Fuzzy extractors derive strong keys from noisy sources.  The goal is to reliably convert a high entropy source~(which may have different values on repeated readings) to the same uniformly key distributed key.  Traditionally, their security is defined information-theoretically.  Fuzzy extractors have upper bounds on the length of the derived key~(Dodis et al., J. of Comp 2008).  In particular, the starting entropy of the source must be significantly higher than the logarithm of number of error patterns corrected.  For many practical noisy sources, like biometrics, this condition is not fulfilled, leaving reliable key derivation from these sources as open problem.

Fuller, Meng, and Reyzin (Asiacrypt 2013) hypothesize that these bounds can be overcome by only providing security against computationally-bounded adversaries.  %They provide a construction of a computational fuzzy extractor that corrects a small number of errors without any loss in key length.  
%They show the feasibility of constructing a computational fuzzy extractor that does not suffer from the information-theoretic bounds.
%Unfortunately, their construction is limited to very high entropy distributions and does not significantly beat information-theoretic bounds.    In addition, we significantly improve on the allowable error rate and the required entropy rate of each block.  In particular we construct the following:
In this work, we provide the first construction of a fuzzy extractor for a large class of distributions where the starting entropy is smaller than the logarithm of the number of correctable error patterns.

\textbf{Construction:} We construct a computational fuzzy extractor based on obfuscation of point functions.  Let $W = W_1, ..., W_\ell$ be a source distribution composed of blocks over a large alphabet, $Z$. To obfuscate a sample $w$ drawn from $W$.  We flip a coin $c_i$ for each block and either obfuscate the block $w_i$ or a random point in $Z$.  When a close reading $w'$ is given as input, we can recover most of the coins $c_i$.  Error-tolerance is achieved by sampling $c = c_1,..., c_\ell$ from an error-correcting code.  Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).  Security holds as long as a large number of blocks $W_i$ of $W$  are unpredictable given equality queries on individual blocks.  Our construction provides the following novel features:
\begin{itemize}
\item The source entropy is smaller than the log of the number of correctable error patterns.  
\item Constant error tolerance rate.  %Previous constructions of computational fuzzy extractors corrected a logarithmic fraction of errors.  (Information-theoretic constructions support a constant fraction of errors but are subject to bounds described above.)
\item Security for a large and meaningful class of distributions.  %The main requirement for security is that most blocks have a super-logarithmic amount of entropy.  Previous computational fuzzy extractors required the source to be essentially uniform. 
\end{itemize}
\end{abstract}

\section{Introduction}\label{sec:introduction}
Reliable key derivation is a cornerstone of authentication.  However, many sources with sufficient entropy for key derivation are noisy and provide similar but not identical values when the source is read multiple times~(examples include biometrics~\cite{daugman2004} and physically unclonable functions~\cite{pappu2002physical}).  To use noisy physical sources in applications, two problems must be addressed.  The first is ensuring the same value is obtained from every reading of the source.  This must be done in a way that does not eliminate all the entropy from the output~(known as information-reconciliation~\cite{bennett1988privacy}).  The second is converting a source with entropy to a uniform random key~(privacy amplification~\cite{bennett1988privacy}).  Both of these problems have interactive and non-interactive versions.  For a single user~(trying to produce the same key from multiple readings of a physical source) the non-interactive versions are appropriate.  We focus on this setting.  %If both of these tasks are achieved a noisy physical source can be used like a uniformly random private key.

Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} perform both tasks non-interactively.  They consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public value $p$.  The second algorithm \rep takes this public value $p$ and a close $w'$ to reproduce the original key $r$.  Traditionally, a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} performs information-reconciliation and a randomness extractor~\cite{nisan1993randomness} performs privacy amplification.

Unfortunately, fuzzy extractors have not yielded key derivation for all noisy sources.  
This is because there is tension between security and error-tolerance.  The key should be uniform to an observer but nearby $w'$ should map to the same key.  By nearby, we mean that $\dis(w, w')\leq t$ for some metric $\dis$.  In the information-theoretic realm, increasing $t$ means a decrease in the strength of the key $r$.  This is because a fuzzy extractor can be converted into an error correcting code~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  The length of $r$ is dictated by size of the best code that corrects $t$ errors.  Error-correcting codes are well studied and we have tight bounds on this quantity. % how many codewords may be in a code that corrects $t$ errors.

 Specifically, we consider the Hamming metric.  For the Hamming metric, the key may be no longer than the difference between the starting entropy of the source\footnote{We assume that the fuzzy extractor operates independently of the source $W$.  As we discuss later, it is possible to avoid these losses if the fuzzy extractor has additional knowledge about the distribution.} and logarithm of the number of error patterns to be corrected. For the remainder of this paper we denote this quantity by $gap$.  This represents a real problem as important biometrics~(such as irises~\cite{daugman2004}) have $gap <0$ and information-theoretic fuzzy extractors provide no security.

 %let $|B_t|$ be the number of points within distance $t$.  The length of the key $|r| < \Hoo(W) - \log |B_t|$~(see~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions).  For the remainder of this paper, we denote this quantity by $gap = \Hoo(W) - \log |B_t|$.

However, this does not need to be the case in the computational setting.  Fuller, Meng, and Reyzin define computational fuzzy extractors.  Computational fuzzy extractors produce pseudorandom instead of truly random keys~\cite{fuller2013computational}.  They hypothesize a computational fuzzy extractor may exist with a small or negative $gap$.  We resolve this question and construct a computational fuzzy extractor when $gap<0$.  This is impossible for an arbitrary min-entropy distribution as every point could be within distance $t$.  A necessary condition for security is that a negligible portion of the probability distribution lies within any Hamming ball of radius $t$.  We require a stronger condition that many blocks are unpredictable~(\defref{def:block guessable}).

The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.  
In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.  Thus, our focus is expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.

\textbf{Overview of Construction:}  Fuller, Meng, and Reyzin~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful.  Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or use a computational version of a fuzzy conductor~(Kanukurthi and Reyzin~\cite{KanukurthiR09} define fuzzy conductors).  Here, we follow the second approach.

Our construction~(\consref{cons:first construction}) is based on obfuscation of point programs.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  A program is obfuscated if nothing is learnable from the program other than its input and output behavior. For a point program, this means hiding all partial information about the point $w$.  Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.

Consider a source $W = W_1,..., W_\ell$ that is split into blocks~(over a large alphabet).  We would like to tolerate errors in $t$ individual blocks.  For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.  With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.  For most locations $i$, \rep can determine whether $w_i$ or a random value was the point obfuscated.  Thus, most bits $c_i$ are recoverable. To tolerate errors we choose the coins $c$ from an error-correcting code.  Then, $c$ forms an extractible distribution of high entropy.  This extraction may be either information-theoretic~\cite{nisan1993randomness} or computation~\cite{DBLP:conf/crypto/Krawczyk10}.  Note, it is hard to recover $w$ from the value $c$.   This is necessary to overcome the information-theoretic lower bounds~\cite[Section 3.3]{fuller2013computational}.

This construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.  
Our construction provides several advantages over previous constructions of computational fuzzy extractors:
\begin{itemize}
\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss in necessary in a fuzzy extractor.  If $W$ consists of points from an error-correcting code of sufficient minimum distance, then no public information is necessary and $gap$ may be negative.  This is not in the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors proceeds by arguing an adversary learns at most a bit for each bit necessary for error correction.   For an arbitrary distribution, this is at least $\log |B_t|$.  The distributions supported by our construction are not error-correcting codes, we only require they are unpredictable in many dimensions~(see \defref{def:block guessable}).}
\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
\item The first computational fuzzy extractor where block are not required to be uniformly distributed.  Our construction simply requires a large number of blocks that are unguessable given equality queries.  This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
\end{itemize}

\textbf{Limitations: } The main limitation of our construction is that each block is individually obfuscated.  This means that blocks much be drawn from distributions with super-logarithmic entropy.  Furthermore, our distance is Hamming distance over a large alphabet~(exponential in the security parameter).  Our construction is applicable for burst errors~\cite{gilbert1960capacity}\bnote{explain?}.  Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.

\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a stronger object than a computational fuzzy extractor).  Unfortunately, this is not the case.  Each block is individually obfuscated, so an adversary may ask equality queries on individual blocks.  If not all blocks have high entropy an adversary may learn significant information about the source.  Thus, our construction is not a virtual black box~(VBB) obfuscation~(where anything learnable by the circuit is simulatable using input/output behavior).  Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} construct noisy point obfuscation for $gap>>0$.  Constructing VBB obfuscation for sources where the error tolerance is smaller than the starting entropy is an important open question.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1,..., X_\ell$ as the concatenation of $X_i$ where each $X_i$ is over some alphabet $\mathcal{Z}$.  For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.  For the Hamming metric, $|B_t| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  Unless otherwise noted logarithms are base $2$.
%\bnote{this is weird here and doesn't fit}  However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).

@@

\subsection{Coding Theory}
\label{sec:coding theory}
We introduce some notions from the field of binary error correcting codes.  Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel\bnote{cite} where there are flips from $0\rightarrow 1$ but no bit flips from $1\rightarrow 0$.  
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$. 
\end{definition}
\textbf{Notes:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes may exist for this type of error.
The class of errors we support~($t$ Hamming errors over a large alphabet) in our source and the class of errors corrected by our code~($t$ $0\rightarrow 1$ errors) are different~(see \consref{cons:first construction} for details).

We need one special property of the code, namely that each output bit is set to $1$ with probability $1/2$.

\begin{lemma}
\label{lem:linear codes independent}
Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
\end{lemma}
Proof in \apref{sec:proof of linear indep}.

\subsection{Obfuscation}
Our construction uses virtual black-box obfuscation of point functions.  This is the following family of functions:
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
\]
Here we present the virtual black-box definition of obfuscation.  See \secref{sec:obfuscation} for a more detailed introduction to obfuscation.  This definition is known to be achievable for point functions under various assumptions~\cite{canetti1997towards, wee2005obfuscating}.  We also need the obfuscation to be $\ell$-composable~(\defref{def:obf comp}).

\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}  
\label{def:obf} Let $\mathcal{C}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
\begin{enumerate}
\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$, 
\[
\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
\]
where the probability is taken over the randomness $r$.  \emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability over the random coin tosses $r$.  Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$, 
and for all binary predicates $\pi$, 
\[
|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
\]
where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.  Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
\end{enumerate}
\end{definition}

\section{Computational Fuzzy Extractors}
\label{sec:fuzzy extractors}

We focus on computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.  Definitions for information-theoretic fuzzy extractors and secure sketches can be found in the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.  The definition of computational fuzzy extractors allows for a small probability of error.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.  
%\begin{definition}
%\label{def:fuzzy extractor}
%An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties: 
%\begin{enumerate}
%\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
%\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
%\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
%\end{enumerate}
%A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
%\end{definition}
%
%Secure sketches are the main technical tool in the construction of fuzzy extractors.  Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
%\begin{definition}
%\label{def:secure sketch}
%An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
%\begin{enumerate}
%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
%\end{definition}
%

@@

\begin{definition}~\cite[Definition 2.5]{fuller2013computational}
\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\kappa$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon$.
\end{itemize}
\end{definition}
In the above definition, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor is designed to work rather than the family of all sources of a given min-entropy $m$.  With $gap<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary.

The work of Fuller, Meng, and Reyzin~\cite{fuller2013computational} presents two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.  We follow the second approach.  
%Our main question is: for what type of sources can we build fuzzy extractors?  Of particular interest are sources where information-theoretic bounds do not allow meaningful constructions~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08}.  The main limiting factor is the difference between the starting entropy and the size of the ball to be corrected or $gap = \Hoo(W) - \log |B_t$.  When $gap$ is large, information-theoretic fuzzy extractors provide a good solution.  We ask whether security is possible when $gap$ is small or negative.
%In this paper, we ask whether a smaller entropy loss can be achieved by considering a computational fuzzy extractor with a computational security requirement.  %We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.
